---
title: "Fitbit"
author: "Marwa"
date: "12/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Hmisc)
library(dplyr)
```

## Activity Monitoring Data

Reading the data 
```{r}
activity <- read.csv("activity.csv")

```

Transforming the data 
```{r}
TotalSteps <- tapply(activity$steps,activity$date,sum, na.rm=TRUE)

```


Plot for steps taken each day

```{r}
hist(TotalSteps)
```

The mean and median total number of steps taken per day
```{r}
Mean <- mean(TotalSteps)
Median <- median(TotalSteps)

Mean
Median

```

Time series plot of the average number of steps taken
```{r}
average_step <- aggregate(steps ~ interval, data = activity, mean, na.rm = TRUE)
plot(average_step$interval, average_step$steps, type = "l", lwd = 2, col = "blue",
     main = "Average Number of Steps Taken", axes =TRUE, 
     xlab = "5-min interval", ylab = "Average no of steps")
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r}
av <- tapply(activity$steps, activity$interval, mean, na.rm = T)
which.max(av)
```
average_steps
Code to describe and show a strategy for imputing missing data
a. the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
length(which(is.na(activity$steps)))
```

b. Imputed values 
```{r}
missingdata_Imputed <- activity
missingdata_Imputed$steps <- impute(activity$steps, fun=mean)
```

plotting a histogram  total number of steps taken each day 
```{r}
TotalStepsImputed <- tapply(missingdata_Imputed$steps,missingdata_Imputed$date,sum, na.rm=TRUE)
hist(TotalStepsImputed)

```

The New median and mean
```{r}
Mean <- mean(TotalStepsImputed)
Median <- median(TotalStepsImputed)

Mean
Median

```

